Kronos \& Krios: Evidence for accretion of a massive, rocky planetary system in a comoving pair of solar-type stars

### 2017-09-14 paper/ms.tex
final edits
- mostly grammar, minor wordings
- appendix finalized

\newcommand{\todo}[1]{{\color{blue}TODO: #1\\}}
\newcommand*{\askjmb}[1]{{\bf #1}}

@@

\begin{abstract}
  We report and discuss the discovery of a comoving pair of bright solar-type
  stars, HD~240430 and HD~240429, with a significant difference in their
  chemical abundances.
  The two stars have an estimated 3D separation of $\approx 0.6$~pc
  ($\approx 0.01$~pc projected) at a distance of
  $r\approx 100~\pc$ with nearly identical three-dimensional velocities,
  %($|\Delta \bs{v}| < XX~\kms$ with 95\% confidence),
  as inferred from \gaia\ \tgas\ parallaxes and proper motions, and
  high-precision radial velocity measurements.
  Stellar parameters determined from high-resolution Keck HIRES spectra
  indicate that both stars are $\sim 4$~Gyr old.
  The more metal-rich of the two, HD~240430, shows an enhancement of refractory
  ($\Tcondens>1200$~K) elements by $\approx 0.2$~dex and a marginal
  enhancement of (moderately) volatile elements ($\Tcondens<1200$~K; \elem{C},
  \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}).
  % TODO: Hmmm...
  This is the largest metallicity difference found in a wide binary pair yet.
  Additionally, HD~240430 shows an anomalously high surface lithium abundance
  ($A(\elem{Li})=2.75$), higher than its companion by $0.5$~dex.
  The proximity in phase-space and ages between the two stars suggests that
  they formed together with the same composition, at odds with the observed
  differences in metallicity and abundance patterns.
  We therefore suggest that the star HD~240430, ``Kronos'', accreted
  \maccreted\ of rocky material after birth, selectively enhancing the
  refractory elements as well as lithium in its surface and convective
  envelope.
\end{abstract}

@@

\sunanalog\ and \bizarreone\ were identified as a
candidate comoving star pair in our recent search for comoving stars using the
proper motions and parallaxes from the \tgas\ catalog, a component of \gaia\ \dr.
We refer the readers to this previous work (\citealt{2017AJ....153..257O}) for a
full explanation of the methodology behind this search and only include
a brief description here.
For a given pair, we compute a marginalized likelihood ratio between the
hypotheses (1) that a given pair of stars share the same 3D velocity vector,
and (2) that they have independent 3D velocity vectors, using only the
astrometric measurements from \tgas\ (parallaxes and proper motions).
We then select a sample of high-confidence comoving pairs by making a
conservative cut on this likelihood ratio.
In the resulting catalog of comoving pairs (\citealt{2017AJ....153..257O}),
the pair presented in this paper was assigned a group id of 1199,
and the marginalized likelihood ratio (Bayes factor)
between the two hypotheses is $\ln{\mathcal{L}_1/\mathcal{L}_2} = 8.52$,
well above the adopted cut value of 6.
The pair has also been previously recognized as a visual double star system
in Washington Double Star catalog (\citealt{2001AJ....122.3466M}).
We have checked that we do not find any possible additional comoving companions
by lowering the likelihood ratio cut for the stars around this pair.

In a separate effort to study detailed chemical abundances of potential
planet-hosting stars, high-resolution spectra of both stars were obtained using
the HIRES spectrograph on the Keck~I telescope, and analyzed
\citep{2016ApJS..225...32B}.
The spectral resolution is $R\approx 70000$ and the wavelength coverage is
$5164$--$7799$~\AA.
A typical signal-to-noise ratio in the spectral continuum is $>200$~per pixel.
The resulting measurements include elemental abundances for 15 chemical species
(C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as well as stellar parameters
and high precision radial velocities.
For the details of the spectral analysis, we refer the readers to
\citealt{2016ApJS..225...32B}.
Additionally, the \elem{Li} doublet at $6707.6$~\AA\
%--- clearly visible in both spectra (see \figname~\ref{fig:spec2}) ---
for this sample was investigated in a separate work (\citealt{jmlithium}).
We list all relevant astrometric and spectroscopic measurements
including the absolute abundance\footnote{
  The absolute abundance of element \elem{X} is
  $A(\elem{X}) = \log_{10} (n_\elem{X}/n_\elem{H})$
  where $n_\elem{X}$ is the number density of element \elem{X}.
}
of \elem{Li} for the two stars in Table~\ref{tab:kk}.

The projected separation between the pair is 1.9\arcmin\ ($\approx 0.01$~pc),
and the 3D separation is $\approx 0.6$~pc.
Although selected based only on their astrometry, the two stars
have identical radial velocities within uncertainties (Table~\ref{tab:kk}),
confirming that they are truly comoving.
Combining these precise radial velocities with the \gaia\ \tgas\ astrometry, we
can compare differences between the inferred 6D phase-space coordinates of the
two stars.
We start by generating posterior samples over the Heliocentric distance, $r$,
tangential velocities, $(v_\alpha, v_\delta)$, and radial velocity, $v_r$,
given the observed parallax, $\hat\pi$, and proper motions,
$(\hat\mu_{\alpha^*}, \hat\mu_\delta)$, and radial velocity, $\hat v_r$.
We assume the noise is Gaussian, and the radial velocity measurement is
uncorrelated with the astrometric measurements.
If we define
\begin{eqnarray}
  \vec{\hat y} &=&
      \transp{\left(
        \begin{array}{c@{\hspace{1em}} c@{\hspace{1em}} c@{\hspace{1em}} c}
          \hat\pi &
          \hat\mu_{\alpha^*} &
          \hat\mu_\delta &
          \hat v_r
        \end{array}
      \right)}\\
  \vec{y} &=&
      \transp{\left(
        \begin{array}{c@{\hspace{1em}} c@{\hspace{1em}} c@{\hspace{1em}} c}
          r^{-1} &
          r^{-1}\,v_\alpha &
          r^{-1}\,v_\delta &
          v_r
        \end{array}
      \right)}
\end{eqnarray}
then the likelihood is
\begin{equation}
  \vec{\hat y} \sim \mathcal{N}(\vec{y}, \mat{C})
\end{equation} where $\mat{C}$ is the covariance matrix.
We adopt a uniform space density prior for the distance and an isotropic
Gaussian for any velocity component, $v$, with a dispersion $\sigma_v=25~\kms$
\begin{eqnarray}
p(r) &=&
  \begin{cases}
    \frac{3}{r_{\rm lim}^3} \, r^2 & \text{if } 0 < r < r_{\rm lim}\\
    0              & \text{otherwise}
  \end{cases}\\
p(v) &=& \frac{1}{\sqrt{2\pi}\,\sigma_v} \,
  \exp\left[-\frac{1}{2} \, \frac{v^2}{\sigma_v^2} \right] \quad .
\end{eqnarray}
%
For each of the two stars, we use \project{emcee}
(\citealt{2013PASP..125..306F}) to generate posterior samples in $(r, v_\alpha,
v_\delta, v_r)$ by running 64 walkers for 4608 steps and discarding the first
512 steps as the burn-in period.
For each sample, we convert the heliocentric phase-space coordinates into
Galactocentric coordinates assuming that the Sun's position and velocity are
$\vec x_\odot = (-8.3,\,0,\,0)~{\rm kpc}$ and $\vec v_\odot =
(-11.1,\,244,\,7.25)~\kms$ \citep[e.g.,][]{Schonrich:2010, Schonrich:2012}.

\figurename~\ref{fig:dxdv} shows differences in posterior samples converted to
Galactocentric phase-space coordinates for the two stars.
The differences in velocities are consistent with zero.
For a 2~\msun\ binary system, the Jacobi radius in the Galactic neighborhood is
1.2~pc (\citealt{Jiang:2010aa}).
Thus, \bizarreone\ and \sunanalog\ are likely a bound system that formed coevally,
and we expect the two stars to have identical metallicities and abundance patterns.
However, one of the stars, \bizarreone\ is significantly more metal
rich than the other (by 0.2~dex $\approx 60\%$; \figname~\ref{fig:abundances}).
Moreover, not all elements are equally enhanced:
the abundances of \bizarreone\ show selective depletion in
\elem{C}, \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}
relative to \elem{Fe}.
\bizarreone\ also has a high surface \elem{Li} abundances, and the difference in
\elem{Li} abundance ($\approx 0.5$~dex) is the largest among all elements
measured.

The validity of the measured abundance differences is further demonstrated in
\figname~\ref{fig:spec1}, \ref{fig:spec2}, and \ref{fig:spec_lithium}, where we
show segments of the spectra and models of the two stars used to measure their
abundances (\citealt{2016ApJS..225...32B}).
As expected from their reported metallicity difference ($\Delta\feh \approx 0.2$),
the ratio of data and model between the two stars show significant
residuals of almost all metal line features, largely dominated by \elem{Fe}.
However, for lines of elements that are not as enhanced in \bizarreone\,
the residuals are much smaller in amplitude (\figname~\ref{fig:spec2}).
The \elem{Li} doublet, analyzed in a separate work (Myles \etal\ in prep.),
is clearly visible in the spectra of both stars, and is stronger in \bizarreone\
(\figname~\ref{fig:spec_lithium}).

We stress that none of the other four twin-like ($\Delta T_\mathrm{eff}
\lesssim 100$~K) wide binary pairs examined by \citealt{2016ApJS..225...32B}
show discrepancies in abundances between the stars at this level.
As shown in \figname~\ref{fig:deltaXH},
the differences in other pairs for all elements except \elem{N} and \elem{O},
which are also the most uncertain (\tablename~\ref{tab:kk}),
are less than $0.05$~dex, making \bizarreone-\sunanalog\ pair a significant outlier.
The statistical uncertainties for each parameter
presented in \tablename~\ref{tab:kk} from \citealt{2016ApJS..225...32B}
are estimated from repeated measurements of multiple spectra of the same stars.
We note that while there may be systematic uncertainties (bias) in the elemental
abundances of these two stars unconstrained by this procedure,
the systematic uncertainties for these two solar-type ``twin-like'' stars
with small differences in $T_\mathrm{eff}$ and $\log{g}$, if any, are unlikely to wash out
the observed abundance differences of $\approx 0.2$~dex.

@@

The surface lithium abundance in a Sun-like star decreases with its age due to
mixing induced by convection or rotation, which brings the lithium into the
interior ($T>2.5 \times 10^{6}$~K) where it will be destroyed by proton capture
burning.
In hotter stars with thin convective zones on the main sequence, most of this
mixing occurs in the pre-main sequence phase when the star is fully convective.
% TODO: REF?
Thus, surface lithium abundance can be an indicator of stellar ages,
especially whether the star is very young ($\lesssim 1$~Gyr).
The absolute $\elem{Li}$ abundance of solar-type stars also correlates steeply
with the effective temperature (e.g., \citealt{Chen2001,2012ApJ...756...46R}).
Generally, cooler stars with larger convective envelope have lower \elem{Li}
abundances.
The absolute $\elem{Li}$ abundance of $2.25$~dex for \sunanalog\
is typical for its \teff.
On the other hand, the lithium abundance ($A(\elem{Li}) = 2.75$) of \bizarreone,
which has lower \teff\ than \sunanalog, is not only higher than that of
\sunanalog\ but also much higher compared to other field stars of similar \teff.
Given the overall higher metal abundances and the peculiar abundance patterns
in \bizarreone, it is unclear, however, whether this higher $\elem{Li}$
abundance means a younger age or something else.
For example, \citealt{Casey:2016aa} attributes the presence of $\elem{Li}$-rich
red giant stars to the engulfment of substellar companions such as gas giant
planets or brown dwarfs which may replenish $\elem{Li}$.

The surface lithium abundance of \bizarreone\ is the only indicator of a
younger age.
If the two stars were only several hundred Myrs old, then
they may have been part of a larger comoving group of stars.
However, as we mention above, there is no evidence in our search of comoving
pairs using \tgas\ that the two stars belong to a larger group of young stars.
Very young stars often show signs of activity such as
X-ray emission from magnetic activity, emission lines, or infrared excess due to
circumstellar disks (\citealt{1999ARA&A..37..363F,1987ApJ...312..788A}).
We have compiled GALEX, Tycho-2, 2MASS, and WISE photometry for these stars,
and found no evidence for indications of activity in their spectral energy
distributions.
%
The low $v\sin(i)$ values (\tablename~\ref{tab:kk}) also argue against very
young ages that would be inferred from the surface lithium abundances.
Finally, we computed the Galactic orbit of the pair using the median of the
posterior sample over the phase space coordinates of \sunanalog, in a Milky
Way-like gravitational potential (similar to \texttt{MWPotential2014} from
\citealt{Bovy:2015}) using \project{Gala} (\citealt{gala}).
The pair's fiducial orbit has a vertical action larger than the Sun, favoring
an older age (\citealt{Wielen:1977,Aumer:2016}).
We therefore conclude that the two stars are most likely coeval, $\sim 4$~Gyr
old main sequence stars, and that the unusually high \elem{Li} abundance of
\bizarreone\ requires an alternative explanation.

@@

While the data described above strongly suggests that the two stars are coeval,
this subsection explores the possibility that this pair is not a primordial
binary.
Two stars unrelated at birth may end up in a binary system via a binary-single
scattering event that results in an exchange of binary members.
In order to estimate the rate at which any binary-single
event will produce a wide binary system such as \sunanalog\ and \bizarreone,
we may consider the rate at which this wide binary will scatter with a field star to
result in an exchange reaction.
The cross-section of exchange scattering for a binary with semi-major axis $a$ is
\begin{eqnarray}
  \sigma_\mathrm{ex} = \frac{640}{81} \pi a^{2} \left(\frac{v_i}{v_c}\right)^{-6}
  \label{eq:crosssection}
\end{eqnarray}
where $v_i$ is the incoming velocity, and $v_c$ is the critical velocity,
defined as
\begin{eqnarray}
  v_c^2 = G \frac{m_1 m_2 (m_1 + m_2 + m_3)}{m_3 (m_1 + m_2)} \frac{1}{a}\,\,.
\end{eqnarray}
\eqname~\ref{eq:crosssection} is appropriate when $v \gg 1$
(\citealt{Hut:1983aa,Hut:1983ab}), which is the case for wide binaries
scattering with field (disk) stars.
If we assume that field stars are made of solar mass stars with a constant
number density $n=1$~pc$^{-3}$, and the incoming velocity of field stars is
$10$~km\,s$^{-1}$, the rate of exchange scattering is
\begin{eqnarray}
  n \sigma_\mathrm{ex} v_i = 6.82\times 10^{-8}\,\mathrm{Gyr}^{-1}
  \frac{n}{\mathrm{pc}^{-3}} \frac{\mathrm{pc}}{a}
  \left(\frac{10~\mathrm{km}\,\mathrm{s}^{-1}}{v_i}\right)^5\,,
\end{eqnarray}
low enough to be negligible.

@@

In this subsection, we explore the hypothesis that chemical inhomogeneity
within the birth cloud is the source of the observed abundance difference.
There is ample evidence against this scenario as most wide binaries show a
difference in \feh\ less than $0.02$~dex
(\citealt{Desidera:2004aa,Gratton:2001aa}.
In the cases in which a significant difference is detected
with high-precision abundance measurements (see \sectionname~\ref{app:review}),
the difference is typically $\sim 0.05$~dex.
Consistent with these results,
none of the other seven similar wide binaries examined in
\citealt{2016ApJS..225...32B} show the same level of differences in abundances.
Though there is generally a larger spread in $\elem{C}$, $\elem{N}$ and
$\elem{O}$, and some pairs show a difference in particular elements as large as
$\approx 0.15$~dex.
The median and maximum \feh\ difference between component stars in the other
seven pairs is $0.02$~dex and $0.09$~dex, respectively.
The differences are even smaller (maximum $\Delta\feh = 0.03$~dex) if we
compare only twin-like ($\Delta T_\mathrm{eff} \lesssim 100$~K) pairs
(\figname~\ref{fig:deltaXH}, black lines).
Thus, a difference of $\approx 0.2$~dex seen in \bizarreone-\sunanalog\ pair is
unlikely to be due to chemical inhomogeneity in the birth cloud.

@@

Another possibility that two coeval stars may end up with different surface
abundances is accretion of planetary material after birth.
In a multi-planet system, dynamical instabilities triggered by planet-planet
scattering (\citealt{1996Sci...274..954R,1996Natur.384..619W}) or encounters with a
field star (\citealt{Malmberg:2011aa}) can lead to planet ejection or accretion.
Indeed, it is an important goal of many exoplanet studies
to detect chemical signatures of planet formation or accretion,
distinguish them from Galactic chemical evolution, and
connect them to theories of evolution of planetary systems.
One approach that is free from confusion with Galactic chemical evolution
is to compare two almost identical stars in a wide binary system.
Assuming that the component stars were born together with identical
initial composition, we may see a difference in their surface abundances
if the two stars then accreted different amounts of planetary material.
The resulting abundance difference may depend on the condensation
temperatures of elements in the protoplanetary disks from which the accreted
planets formed, as their compositions depend on the radial temperature gradient
in the disk.
%TODO: cautions on condensation temperature
% 1. it is just a proxy
% 2. it is **equlibrium** condensation temperature

In Figure~\ref{fig:relabun_tcrank}, we show the abundance difference
between \bizarreone\ and \sunanalog\ ordered by the rank of \Tcondens\
of each element.
The equilibrium condensation temperatures for the composition of solar system
are taken from \citealt{2003ApJ...591.1220L} (Table~8).
The difference seen in \bizarreone-\sunanalog\ is
compared to HD~20781/2, XO-2N/S, WASP-94A/B in \figname~\ref{fig:relabun_tcrank}.
The metallicity difference of $\approx 0.2$~dex observed in this pair
is larger than the differences seen in any other pairs studied so far.
The five under-enhanced elements in \bizarreone\
relative to \sunanalog\ are the five most volatile in all elements measured.
The difference in \elem{Mn} ($\Tcondens = 1158$~K) and
\elem{Cr} ($\Tcondens = 1296$~K) suggests a break in $\Tcondens \approx 1200$~K.
This $\Tcondens$-dependent trend of $\Delta\elemH{X}$,
combined with the enhanced $\elem{Li}$ abundance ($A(\elem{Li}) = 2.75$),
strongly suggests that accretion of rocky material has occurred in \bizarreone.

>>>>

\newcommand{\todo}[1]{{\color{blue}TODO: #1\\}}

@@

\begin{abstract}
  We report and discuss the discovery of a comoving pair of bright solar-type
  stars, HD~240430 and HD~240429, with a significant difference in their
  chemical abundances.
  The two stars have an estimated 3D separation of $\approx 0.6$~pc
  ($\approx 0.01$~pc projected) at a distance of
  $r\approx 100~\pc$ with nearly identical three-dimensional velocities,
  %($|\Delta \bs{v}| < XX~\kms$ with 95\% confidence),
  as inferred from \gaia\ \tgas\ parallaxes and proper motions, and
  high-precision radial velocity measurements.
  Stellar parameters determined from high-resolution Keck HIRES spectra
  indicate that both stars are $\sim 4$~Gyr old.
  The more metal-rich of the two, HD~240430, shows an enhancement of refractory
  ($\Tcondens>1200$~K) elements by $\approx 0.2$~dex and a marginal
  enhancement of (moderately) volatile elements ($\Tcondens<1200$~K; \elem{C},
  \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}).
  This is the largest metallicity difference found in a wide binary pair yet.
  Additionally, HD~240430 shows an anomalously high surface lithium abundance
  ($A(\elem{Li})=2.75$), higher than its companion by $0.5$~dex.
  The proximity in phase-space and ages between the two stars suggests that
  they formed together with the same composition, at odds with the observed
  differences in metallicity and abundance patterns.
  We therefore suggest that the star HD~240430, ``Kronos'', accreted
  \maccreted\ of rocky material after birth, selectively enhancing the
  refractory elements as well as lithium in its surface and convective
  envelope.
\end{abstract}

@@

\sunanalog\ and \bizarreone\ were identified as a candidate comoving star pair
in our recent search for comoving stars using the proper motions and parallaxes
from the Tycho-Gaia Astrometric Solution catalog (\tgas), a component of \gaia\
\dr.
We refer the readers to this previous work (\citealt{2017AJ....153..257O}) for a
full explanation of the methodology behind this search and only include
a brief description here.
For a given pair, we compute the marginalized likelihood ratio between the
hypotheses (1) that a given pair of stars share the same 3D velocity vector,
and (2) that they have independent 3D velocity vectors, using only the
astrometric measurements from \tgas\ (parallaxes and proper motions).
We then select a sample of high-confidence comoving pairs by making a
conservative cut on this likelihood ratio.
In the resulting catalog of comoving pairs (\citealt{2017AJ....153..257O}),
the pair presented in this paper was assigned a group id of 1199,
and the marginalized likelihood ratio (Bayes factor)
between the two hypotheses is $\ln{\mathcal{L}_1/\mathcal{L}_2} = 8.52$,
well above the adopted cut value of 6.
The pair has also been previously recognized as a visual double star system
in Washington Double Star catalog (\citealt{2001AJ....122.3466M}).
We have checked that we do not find any possible additional comoving companions
by lowering the likelihood ratio cut for the stars around this pair.

In a separate effort to study detailed chemical abundances of potential
planet-hosting stars, high-resolution spectra of both stars were obtained using
the HIRES spectrograph on the Keck~I telescope, and analyzed
\citep{2016ApJS..225...32B}.
The spectral resolution is $R\approx 70000$ and the wavelength coverage is
$5164$--$7799$~\AA.
A typical signal-to-noise ratio in the spectral continuum is $>200$~per pixel.
The resulting measurements include elemental abundances for 15 chemical species
(C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as well as stellar parameters
and high precision radial velocities.
For the details of the spectral analysis, we refer the readers to
\citealt{2016ApJS..225...32B}.
Additionally, the \elem{Li} doublet at $6707.6$~\AA\
%--- clearly visible in both spectra (see \figname~\ref{fig:spec2}) ---
for this sample was investigated in a separate work (\citealt{jmlithium}).
We list all relevant astrometric and spectroscopic measurements including the
absolute abundances of \elem{Li} for the two stars in Table~\ref{tab:kk}.

The projected separation between the pair is 1.9\arcmin\ ($\approx 0.01$~pc),
and the 3D separation is $\approx 0.6$~pc.
Although selected based only on their astrometry, the two stars
have identical radial velocities within their uncertainties (Table~\ref{tab:kk}),
confirming that they are truly comoving.
Combining these precise radial velocities with the \gaia\ \tgas\ astrometry, we
can compare differences between the inferred 6D phase-space coordinates of the
two stars.
We start by generating posterior samples over the Heliocentric distance, $r$,
tangential velocities, $(v_{\alpha^*}, v_\delta)$, and radial velocity, $v_r$,
given the observed parallax, $\hat\pi$, proper motions,
$(\hat\mu_{\alpha^*}, \hat\mu_\delta)$, and radial velocity, $\hat v_r$
\footnote{$\alpha^*$ denotes the projection in right ascension direction,
  i.e., $\mu_{\alpha^*} = \dot\alpha \cos\delta$.
}.
We assume the noise is Gaussian, and the radial velocity measurements are
uncorrelated with the astrometric measurements.
If we define
\begin{eqnarray}
  \vec{\hat y} &=&
      \transp{\left(
        \begin{array}{c@{\hspace{1em}} c@{\hspace{1em}} c@{\hspace{1em}} c}
          \hat\pi &
          \hat\mu_{\alpha^*} &
          \hat\mu_\delta &
          \hat v_r
        \end{array}
      \right)}\\
  \vec{y} &=&
      \transp{\left(
        \begin{array}{c@{\hspace{1em}} c@{\hspace{1em}} c@{\hspace{1em}} c}
          r^{-1} &
          r^{-1}\,v_\alpha &
          r^{-1}\,v_\delta &
          v_r
        \end{array}
      \right)}
\end{eqnarray}
then the likelihood is
\begin{equation}
  \vec{\hat y} \sim \mathcal{N}(\vec{y}, \mat{C})
\end{equation} where $\mat{C}$ is the covariance matrix.
We adopt a uniform space density prior for the distance and an isotropic
Gaussian for any velocity component, $v$, with a dispersion $\sigma_v=25~\kms$
\begin{eqnarray}
p(r) &=&
  \begin{cases}
    \frac{3}{r_{\rm lim}^3} \, r^2 & \text{if } 0 < r < r_{\rm lim}\\
    0              & \text{otherwise}
  \end{cases}\\
p(v) &=& \frac{1}{\sqrt{2\pi}\,\sigma_v} \,
  \exp\left[-\frac{1}{2} \, \frac{v^2}{\sigma_v^2} \right] \quad .
\end{eqnarray}
%
For each of the two stars, we use \project{emcee}
(\citealt{2013PASP..125..306F}) to generate posterior samples in $(r, v_\alpha,
v_\delta, v_r)$ by running 64 walkers for 4608 steps and discarding the first
512 steps as the burn-in period.
For each sample, we convert the heliocentric phase-space coordinates into
Galactocentric coordinates assuming that the Sun's position and velocity are
$\vec x_\odot = (-8.3,\,0,\,0)~{\rm kpc}$ and $\vec v_\odot =
(-11.1,\,244,\,7.25)~\kms$ \citep[e.g.,][]{Schonrich:2010, Schonrich:2012}.

\figurename~\ref{fig:dxdv} shows differences in posterior samples converted to
Galactocentric phase-space coordinates for the two stars.
The differences in velocities are consistent with zero.
For a 2~\msun\ binary system, the Jacobi radius in the Solar neighborhood is
1.2~pc (\citealt{Jiang:2010aa}).
Thus, \bizarreone\ and \sunanalog\ are likely a bound system that formed coevally,
and we expect the two stars to have identical metallicities and abundance patterns.
However, one of the stars, \bizarreone\ is significantly more metal
rich than the other by 0.2~dex ($\approx 60\%$; \figname~\ref{fig:abundances}).
Moreover, not all elements are equally enhanced:
the abundances of \bizarreone\ show selective depletion in
\elem{C}, \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}
relative to \elem{Fe}.
\bizarreone\ also has a high surface \elem{Li} abundances, and the difference in
\elem{Li} abundance ($\approx 0.5$~dex) is the largest among all elements
measured.

The validity of the measured abundance differences is further demonstrated in
\figname~\ref{fig:spec1}, \ref{fig:spec2}, and \ref{fig:spec_lithium}, where we
show segments of the spectra and models of the two stars used to measure their
abundances (\citealt{2016ApJS..225...32B}).
As expected from their reported metallicity difference ($\Delta\feh \approx 0.2$),
the ratio of data and model between the two stars show significant
residuals for almost all metal line features, largely dominated by \elem{Fe}.
However, for lines of elements that are not as enhanced in \bizarreone\,
the residuals are much smaller in amplitude (\figname~\ref{fig:spec2}).
The \elem{Li} doublet, analyzed in a separate work (Myles \etal\ in prep.),
is clearly visible in the spectra of both stars, and is stronger in \bizarreone\
(\figname~\ref{fig:spec_lithium}).

We stress that none of the other four twin-like ($\Delta T_\mathrm{eff}
\lesssim 100$~K) wide binary pairs examined by \citealt{2016ApJS..225...32B}
show discrepancies in abundances between the stars at this level.
As shown in \figname~\ref{fig:deltaXH},
the differences in other pairs for all elements except \elem{N} and \elem{O},
which are also the most uncertain (\tablename~\ref{tab:kk}),
are less than $0.05$~dex, making \bizarreone-\sunanalog\ pair a significant outlier.
The statistical uncertainties for each parameter
presented in \tablename~\ref{tab:kk} from \citealt{2016ApJS..225...32B}
are estimated from repeated measurements of multiple spectra of the same stars.
We note that while there may be systematic uncertainties (bias) in the elemental
abundances of these two stars unconstrained by this procedure,
the systematic uncertainties, if any, for these two solar-type ``twin-like'' stars
with small differences in $T_\mathrm{eff}$ and $\log{g}$ are unlikely to wash out
the observed abundance differences of $\approx 0.2$~dex.

@@

The surface lithium abundance in a Sun-like star decreases with its age due to
mixing induced by convection or rotation, which brings the lithium into the
interior ($T>2.5 \times 10^{6}$~K) where it will be destroyed by proton capture
burning.
In hotter stars with thin convective zones on the main sequence, most of this
mixing occurs in the pre-main sequence phase when the star is fully convective.
Thus, surface lithium abundance can be an indicator of stellar ages,
especially whether the star is very young ($\lesssim 1$~Gyr).
The absolute $\elem{Li}$ abundance of solar-type stars also correlates steeply
with the effective temperature (e.g., \citealt{Chen2001,2012ApJ...756...46R}).
Generally, cooler stars with larger convective envelope have lower \elem{Li}
abundances.
The absolute $\elem{Li}$ abundance of $2.25$~dex for \sunanalog\
is typical for its \teff.
On the other hand, the lithium abundance ($A(\elem{Li}) = 2.75$) of \bizarreone,
which has lower \teff\ than \sunanalog, is not only higher than that of
\sunanalog\ but also much higher compared to other field stars of similar \teff.
Given the overall higher metal abundances and the peculiar abundance patterns
in \bizarreone, it is unclear, however, whether this higher $\elem{Li}$
abundance means a younger age or something else.
For example, \citealt{Casey:2016aa} attributes the presence of $\elem{Li}$-rich
red giant stars to the engulfment of substellar companions such as gas giant
planets or brown dwarfs which may replenish $\elem{Li}$.

The surface lithium abundance of \bizarreone\ is the only indicator of a
younger age.
If the two stars were only several hundred Myrs old, then
they may have been part of a larger comoving group of stars.
However, as we mention above (\sectionname~\ref{sec:data}), there is no
evidence in our search of comoving pairs using \tgas\ that the two stars belong
to a larger group of young stars.
Very young stars often show signs of activity such as
X-ray emission from magnetic activity, emission lines, or infrared excess due to
circumstellar disks (\citealt{1999ARA&A..37..363F,1987ApJ...312..788A}).
We have compiled GALEX, Tycho-2, 2MASS, and WISE photometry for these stars,
and found no evidence for indications of activity in their spectral energy
distributions.
%
The low $v\sin(i)$ values (\tablename~\ref{tab:kk}) also argue against very
young ages that would be inferred from the surface lithium abundance.
Finally, we computed the Galactic orbit of the pair using the median of the
posterior sample over the phase-space coordinates of \sunanalog, in a Milky
Way-like gravitational potential (similar to \texttt{MWPotential2014} from
\citealt{Bovy:2015}) using \project{Gala} (\citealt{gala}).
The pair's fiducial orbit has a vertical action larger than the Sun, favoring
an older age (\citealt{Wielen:1977,Aumer:2016}).
We therefore conclude that the two stars are most likely coeval, $\sim 4$~Gyr
old main sequence stars, and that the unusually high \elem{Li} abundance of
\bizarreone\ requires an alternative explanation.

@@

While the data described above strongly suggests that the two stars are coeval,
this subsection explores the possibility that this pair is still not a
primordial binary.
Two stars unrelated at birth may end up in a binary system via a binary-single
scattering event that results in an exchange of binary members.
In order to estimate the rate at which any binary-single
event will produce a wide binary system such as \sunanalog\ and \bizarreone,
we may consider the rate at which this wide binary will scatter with a field star to
result in an exchange reaction.
The cross-section of exchange scattering for a binary with semi-major axis $a$ is
\begin{eqnarray}
  \sigma_\mathrm{ex} = \frac{640}{81} \pi a^{2} \left(\frac{v_i}{v_c}\right)^{-6}
  \label{eq:crosssection}
\end{eqnarray}
where $v_i$ is the incoming velocity, and $v_c$ is the critical velocity,
defined as
\begin{eqnarray}
  v_c^2 = G \frac{m_1 m_2 (m_1 + m_2 + m_3)}{m_3 (m_1 + m_2)} \frac{1}{a}\,\,.
\end{eqnarray}
\eqname~\ref{eq:crosssection} is appropriate when $v_i/v_c \gg 1$
(\citealt{Hut:1983aa,Hut:1983ab}), which is the case for wide binaries
scattering with field (disk) stars.
If we assume that field stars are made of solar-mass stars with a constant
number density $n=1$~pc$^{-3}$, and the incoming velocity of field stars is
$10$~km\,s$^{-1}$, the rate of exchange scattering is
\begin{eqnarray}
  n \sigma_\mathrm{ex} v_i = 6.82\times 10^{-8}\,\mathrm{Gyr}^{-1}
  \frac{n}{\mathrm{pc}^{-3}} \frac{\mathrm{pc}}{a}
  \left(\frac{10~\mathrm{km}\,\mathrm{s}^{-1}}{v_i}\right)^5\,,
\end{eqnarray}
low enough to be negligible.

@@

In this subsection, we explore the hypothesis that chemical inhomogeneity
within the birth cloud is the source of the observed abundance difference.
There is ample evidence against this scenario as most wide binaries show a
difference in \feh\ less than $0.02$~dex
(\citealt{Desidera:2004aa,Gratton:2001aa}).
Even when a significant difference is detected with high-precision abundance
measurements, the difference is typically $\sim 0.05$~dex (see
\figname~\ref{fig:relabun_tcrank} and \sectionname~\ref{app:review}).
Consistent with these results, none of the other seven similar wide binaries
examined in \citealt{2016ApJS..225...32B} show such large differences in
abundances though there is generally a larger spread in $\elem{C}$, $\elem{N}$
and $\elem{O}$, and some pairs show a difference in particular elements as
large as $\approx 0.15$~dex.
The median and maximum \feh\ difference between component stars in the other
seven pairs is $0.02$~dex and $0.09$~dex, respectively.
The differences are even smaller (maximum $\Delta\feh = 0.03$~dex) if we
compare only twin-like ($\Delta T_\mathrm{eff} \lesssim 100$~K) pairs
(\figname~\ref{fig:deltaXH}, black lines).
Thus, a difference of $\approx 0.2$~dex seen in \bizarreone-\sunanalog\ pair is
unlikely to be due to chemical inhomogeneity in the birth cloud.

@@

Another possibility that two coeval stars may end up with different surface
abundances is accretion of planetary material after birth.
In a multi-planet system, dynamical instabilities triggered by planet-planet
scattering (\citealt{1996Sci...274..954R,1996Natur.384..619W}) or encounters with a
field star (\citealt{Malmberg:2011aa}) can lead to planet ejection or accretion.
Indeed, it is an important goal of many exoplanet studies
to detect chemical signatures of planet formation or accretion,
distinguish them from Galactic chemical evolution, and
connect them to theories of evolution of planetary systems.
One approach that is free from confusion with Galactic chemical evolution
is to compare two almost identical stars in a wide binary system.
Assuming that the component stars were born together with identical
initial composition, we may see a difference in their surface abundances
if the two stars then accreted different amounts of planetary material.
The resulting abundance difference may depend on the condensation
temperatures of elements in the protoplanetary disks from which the accreted
planets formed, as their compositions depend on the radial temperature gradient
in the disk.

In Figure~\ref{fig:relabun_tcrank}, we show the abundance difference
between \bizarreone\ and \sunanalog\ ordered by the rank of \Tcondens\
of each element.
The equilibrium condensation temperatures for the composition of solar system
are taken from \citealt{2003ApJ...591.1220L} (Table~8).
The difference seen in \bizarreone-\sunanalog\ is
compared to HD~20781/2, XO-2N/S, WASP-94A/B in \figname~\ref{fig:relabun_tcrank}.
The metallicity difference of $\approx 0.2$~dex observed in this pair
is larger than the differences seen in any other pairs studied so far
(see also Appendix~\ref{app:review}).
The five under-enhanced elements in \bizarreone\
relative to \sunanalog\ are the five most volatile in all elements measured.
The difference in \elem{Mn} ($\Tcondens = 1158$~K) and
\elem{Cr} ($\Tcondens = 1296$~K) suggests a break in $\Tcondens \approx 1200$~K.
This $\Tcondens$-dependent trend of $\Delta\elemH{X}$,
combined with the enhanced $\elem{Li}$ abundance ($A(\elem{Li}) = 2.75$),
strongly suggests that accretion of rocky material has occurred in \bizarreone.
